---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# elixir4r (WIP)

The package provides R interface to [elixir](https://elixir-lang.org/)

## Installation

You can install the development version of elixir4r via: 

``` r
devtools::install_github("enixam/elixir4r")
```

## Example

First load the package

```{r}
library(elixir4r)
```

### Interfaces 

Evaluate inline elixir code 

```{r}
ex_eval("
defmodule Test do
  def main, do: IO.puts(:ok)
end 

Test.main()
")
```

Run `.exs` script 

```{r}
code <- "IO.write(['hello ', 'R'])"
tmp <- tempfile()
cat(code, file = tmp)
ex_run(tmp)
```



### R Markdown 

After `library`, elixir4r will register a custom knitr engine `elixir`. 

Insert an `elixir` chunk 

````
```{elixir}`r ''`
{{year, month, day}, {hour, _, _}} = :calendar.local_time()
IO.puts("hello world from #{year}/#{month}/#{day} #{hour} o'clock") 
```
````


This yields 

```{elixir, echo = FALSE}
{{year, month, day}, {hour, _, _}} = :calendar.local_time()

IO.puts("hello world from #{year}/#{month}/#{day} #{hour} o'clock")
```


The last line of the code block gets automatically printed by `IO.inspect`

```{elixir}
m = %{name: "elixir", creator: "José Valim", status: :nice}
m
```


